---
title: "My Final Project -Dynamic"
runtime: shiny
author: "Gabe Appelbaum"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: menu
    theme: united
# run rsconnect::deployApp()
---

```{r global, include=FALSE}
library(flexdashboard)
library(rtweet)
library(leaflet)
library(quanteda)
library(quanteda.textstats)
library(quanteda.textplots)
library(igraph)
library(visNetwork)
library(scales)
library(highcharter)
library(lubridate)
library(reshape2)
library(dplyr)
library(syuzhet) 
library(stringr)
library(tidyr)
library(DT)

load(file="tweets.rda")
load(file="senti_aggregated_tweets.rda")
```

Inputs {.sidebar}
====================================================================

```{r}
h5("Data updated:", Sys.Date())

checkboxGroupInput("sentiment1", 
                   label = (helpText(h5("Choose sentiments"))),
                    choices = list("Anger" = "anger", 
                    "Anticipation" = "anticipation",
                    "Disgust" = "disgust",
                    "Fear" = "fear",
                    "Joy" = "joy", 
                    "Sadness" = "sadness", 
                    "Surprise" = "surprise",
                    "Trust" = "trust"),
                   selected = list("surprise","trust","anger"))

selectInput("language", label = (helpText(h5(strong("Choose a language")))),
            choices = list("English" = "en",
                           "French" = "fr",
                           "Spanish" = "es",
                           "German" = "de",
                           "Chinese" = "zh",
                           "Arabic" = "ar",
                           "Russian" = "ru",
                           "Turkish" = "tr"),
            selected = "en"
)


```
Sentiments {data-orientation=scroll data-icon="fa-bar-chart"}
=======================================================================

### 
###

### **Introducing Sentiment Analysis based on tweets about Elon Musk over this two day period**

The sentiment detection algorithm detects *anger*, *anticipation*, *disgust*, *fear*, *joy*, *sadness*, *surprise*, and *trust*. 

### Row 1 {data-height=110}
-----------------------------------------------------------------------

```{r}

senti_aggregated$date_label <- as.Date(senti_aggregated$date_label)

output$chart <- renderHighchart({

  highchart() %>%
    hc_add_series(data= senti_aggregated[senti_aggregated$variable %in% input$sentiment1,],"line", hcaes(x = date_label, y = value,                                                                 group=variable)) %>%
hc_xAxis(type = "datetime")

})

highchartOutput('chart')

```

Hashtags {data-orientation=scroll data-icon="fa-bar-chart"}
=======================================================================

### **Introducing hashtag networks by language based on tweets about Elon Musk**

These tweets are ones that use the phrase "elon musk" they are not all neccessarily connected to a certain hashtag.

```{r}
renderPlot({
  corpus <- corpus(tweets[tweets$lang == input$language,],docid_field = "id_str",text_field = "full_text")
  
  tweets_dfm <- tokens(corpus, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_url=TRUE) %>%  
  dfm()
  
  tag_dfm <- dfm_select(tweets_dfm, pattern = "#*")
  toptag <- names(topfeatures(tag_dfm, 1000))
  tag_fcm <- fcm(tag_dfm)
  topgat_fcm <- fcm_select(tag_fcm, pattern = toptag)
  textplot_network(topgat_fcm, min_freq = 0.01, edge_alpha = 4, edge_size = .8, edge_color = "yellow")

})

```

Map {data-orientation=scroll data-icon="fa-bar-chart"}
=======================================================================

### **Introducing a geomap of tweets about Elon Musk by language, some interesting trends are revealed by the tone of different tweets in different locations**

This is a map of tweets about Elon Musk sorted by language. It is clear from geomapping and that english is the most common that America is the place with the most twitter based discussions of Elon Musk. Interestingly the map seems to show how Musk has gained and lost favor along political lines. Tweets tagged to traditionally Republican areas, such as Texas, tend to mention Musk in a positive light and those same tweets tend to echo current Republican talking points. The same is true for tweets from traditionally Democratic areas, such as New York City, that view Musk less favorably and tend to echo some Democratic talking points.

While the sample size here is small and the evidence is anectdotal this does suggest some interesting trends in which groups are in support of Musk and which aren't.

```{r}

renderLeaflet({
  geocodes <- lat_lng(tweets[tweets$lang == input$language,])
  geocodes <- geocodes[!is.na(geocodes$lat),]

  map <- leaflet(data = geocodes) %>% 
  addTiles() %>%
  setView(lng = 39, lat = 34, zoom = 2) %>% 
  addMarkers(lng = ~lng, lat = ~lat,popup = ~ as.character(text)) %>% 
  addProviderTiles(providers$Esri.WorldStreetMap) %>% #select basemap template
  addCircleMarkers(stroke = TRUE, fillOpacity = 0.3) 
  
  map

})


```

